%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
\name{Xinyu}{Gao}
\position{Software Engineer{\enskip\cdotp\enskip}Data Engineer}
\address{U1/1 Haradli Court, Launceston TAS 7250, Australia (open to relocate)}

\mobile{(+61) 452512419}
\email{xinyu.gao96@gmail.com}
%\dateofbirth{January 1st, 1970}
\github{victorgaoxinyu}
\linkedin{xinyu-gao}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Macquarie Group Limited\\
           50 Martin Place\\
           Sydney NSW 200}
  {}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer - Python}
% How the letter is opened
\letteropening{Dear Hiring Manager}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Xinyu Gao~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am writing to express my keen interest in Software Engineer - Python at Macquarie, referred to me by an ex-colleague. With a strong background in data-focused python development, and extensive experience in cloud computing, I am excited about the opportunity to contribute to your team.

In my current role as Algorithm Performance Engineer at Seeing Machines, I lead the development of new internal tools, maintain and optimize our Python and C++ codebase, specialized in data analytics, visualization, and project management. I am instrumental in drafting data collection protocols and collaborate closely with algorithm developers to refine and validate our technology. This includes reviewing pilot data, performing sanity checks, and establishing evaluation metrics. Additionally, I manage external communications, effectively presenting our algorithms' performance to clients through detailed validation reports and supporting project managers in client interactions. My ability to translate technical details into client-friendly language and incorporate customer feedback into our development process is a testament to my commitment to continuous improvement and effective project communication.

I played a pivotal role in designing our petabyte-scale complex dataset, analyzing usage patterns across various user backgrounds. This led to the development of a dual-faceted solution: a Data API for developers to integrate into their workflows, and a user-friendly interface, like a file explorer or webpage for non-technical users. Additionally, I designed and implemented a data usage monitoring system with Grafana and Prometheus, gauging different departments' data access patterns to assist IT allocate resource accordingly.

My expertise in software engineering is further demonstrated through my leadership in the development of an Automated Data Analysis System. This initiative streamlined our operations by automating repetitive reporting tasks, thus freeing the team to concentrate on sophisticated R\&D initiatives. Utilizing Python, I integrated a bespoke framework that encompasses data processing and validation into our Jenkins CI pipeline. This setup leverages both local processing nodes and AWS EC2 instances, optimizing the processing of cloud-stored data. Additionally, I played a crucial role in migrating an existing data processing tool from Pandas to PySpark, significantly improving scalability and efficiency for processing terabyte-level datasets.

I am also experienced in cloud-based computing, particularly in using AWS for data analysis and ETL tasks. In a key project for an EU client, I spearheaded the development of a data transfer pipeline that employs the AWS Boto3 API for effective data movement across regions. Additionally, I developed a bespoke C++ image extraction tool tailored to the client's technical specifications. This tool extracts image pixel information from customer's encrypted data, underscoring my capability to provide custom solutions that precisely meet client requirements. I also crafted configurable container images featuring robust entry-point scripts that enable seamless data conversion and integration using AWS Batch, significantly enhancing processing efficiency.

My experience extends to leading customer-facing projects, providing technical support, and using complex data analysis to drive business development. In one of my key projects, I employed data science techniques to influence a significant commercial decision. Tasked with enhancing the accuracy of our driver monitoring algorithm, I faced the challenge of convincing a client to modify the 3D models of the car cabin components, like the rear-view mirror, to improve algorithmic performance. By analyzing drivers' gaze directions and re-projecting them onto a 3D heatmap with Plotly, I demonstrated that when drivers claimed to be looking at the center of the mirror, their focus actually scattered around that point. This insight led me to advocate for enlarging the hit zone of the mirror beyond its physical dimensions. This data-driven approach successfully persuaded the client to adjust their design, showcasing my ability to use data science to drive operational improvements and commercial success.

In my spare time, I enjoy engaging in a variety of sports, including running, mountain biking, climbing and paddling. These hobbies not only keep me physically active, but also enhance my focus on both professional and personal endeavors. 

Thank you for considering my application. I am looking forward to the opportunity to further discuss how I can contribute to your team.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
