%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Algorithm Performance Engineer} % Job title
    {Seeing Machines Limited} % Organization
    {Canberra, Australia} % Location
    {Dec. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead the development of Industrial-grade automated performance testing pipeline, enhancing data visualization and user engagement.}
        \item {Maintain and improve data validation framework, streamlining code base through decoupling and abstraction.}
        \item {Implement data processing pipeline with PySpark, incorporate custom functions with Pandas and }
        \item {Develope C++ tool to support image extraction process with automotive OEMs}
        \item {Optimized Jenkin CI/CD pipeline, reduce build time by 60\% through the adoption of containerized environments and test sequence reorganization.}
        \item {Manage PB level datasets, support data collection protocol drafting and offer insights for algorithmic enhancements, notably in gaze tracking.}
        \item {Design and implement data usage monitoring system, enhancing IT resource management through user behaviour analysis.}
        \item {Provide statistical analysis for multiple automotive projects, maintain strong relationships with Tier 1 and OEM partners.}
        \item {Collaborate with technical write to create training documents for automotive technicians.}
        \item {Mentor junor members and contractors, enhance team productivity and forster skill development.}
        \item {Python, C++, Shell, AWS (S3, EC2, Batch, Lambda), Docker, Git, Jenkins, Grafana}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Student} % Job title
    {Australian National University} % Organization
    {Canberra, Australia} % Location
    {Nov. 2018 - Feb. 2019} % Date(s)
    {
      \begin{cvitems}
        \item {Conducted in-depth data analysis on power grid dataset, analyze power usage pattern.}
        \item {Maintain internal API development.}
        \item {Authored conference paper "The NextGen Energy Storage trial in the ACT, Australia", highlighting the application of data science in energy consumption analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {National Tainwan Ocean University} % Organization
    {Keelung, Taiwan} % Location
    {Jul. 2016 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design new shape of metal and gain material to enhance acousto-optic interaction.}
        \item {Modulate nano laser resonate wavelength by applying surface acoustic wave perturbation.}
        \item {Design plasmonic nano laser strucure with high Purcell factor and light extraction efficiency.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {National Taiwan Ocean University} % Organization
    {Keelung, Tainwan} % Location
    {Jul. 2016 - Jun 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provide instruction in conjunction with teacher for "Enterprise and Management" Course.}
        \item {Prepare lecture material, answer class questions, and issue guidance for student project work.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
